Analysis of Bauer et al. (unpublished) Field experiment: <br> Recovery completeness

### 2023-03-01 R/model_check_recovery_check.Rmd
Update model_check_recovery_check.Rmd

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE
  )
```
<br/>
<br/>
<b>Markus Bauer</b>

@@

```{r loo}
loo1
loo2
plot(loo1)
plot(loo2)
```

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  echo = TRUE
  )
```

<br/> <br/> <b>Markus Bauer</b>

@@

```{r loo}
# Leave-one-out cross validation based on posterior likelihood
loo1 <- m_1 %>% brms::loo(save_psis = TRUE, moment_match = FALSE)
loo2 <- m_2 %>% brms::loo(save_psis = TRUE, moment_match = FALSE)
loo1
loo2
plot(loo1)
plot(loo2)
```
